### 2013-09-20 exact_learning/paper.tex
Helvetica, Titel neu setzen, korrekturen einarbeiten.

As using LP relaxations was considered too costly for typical computer vision
approaches, later work employed graph-cuts~\citep{szummer2008learning} or Loopy
Believe Propagation (LBP)~\citep{lucchi2011spatial}. These works use a single
inference algorithm for the whole learning process, and can not provide any
bounds on the true objective or the empirical risk. In contrast, in this chapter
we show how to combine different inference methods that are more appropriate
for different stages of learning.

@@

While using more different oracles is certainly possible, we found
that using just these three methods performed very well in practice.  This
combination allows us to make fast progress initially and guarantee optimality
in the end. Our strategy is visualized in \Figref{scheme_inference_algs}
Notably, it is not necessary for an algorithm used as 3) to always produce
exact results. For guaranteeing optimality of the model, it is sufficient that
we obtain a certificate of optimality when learning stops.
% TODO certify optimality != exact...

>>>>

As using LP relaxations was considered too costly for typical computer vision
approaches, later work employed graph-cuts~\citep{szummer2008learning} or Loopy
Belief Propagation (LBP)~\citep{lucchi2011spatial}. These works use a single
inference algorithm for the whole learning process, and can not provide any
bounds on the true objective or the empirical risk. In contrast, in this chapter
we show how to combine different inference methods that are more appropriate
for different stages of learning.

@@

While using more different oracles is certainly possible, we found
that using just these three methods performed very well in practice.  This
combination allows us to make fast progress initially and guarantee optimality
in the end. Our strategy is visualized in \Figref{scheme_inference_algs}.
Notably, it is not necessary for an algorithm used as the third strategy to
always produce exact results. For guaranteeing optimality of the model, it is
sufficient that we obtain a certificate of optimality when learning stops.
% TODO certify optimality != exact...

### 2013-09-20 itm/paper.tex
Helvetica, Titel neu setzen, korrekturen einarbeiten.

Clustering algorithms based on minimum spanning trees have been studied early
on in the statistics community, due to their efficiency.  One of the earliest
methods is single-link agglomerative clustering~\citep{gower1969minimum}.
Single-link agglomerative clustering can be understood as a minimum spanning
tree-based approach in which the largest edge is removed until the desired
number of components is reached.  \citet{zahn1971graph} refines this criterion
by cutting edges that are longer than other edges in the vicinity. This
approach requires tuning several constants by hand. More recently,
\citet{grygorash2006minimum} proposed a hierarchical MST-based clustering
approach that iteratively cuts edges, merges points in the resulting
components, and rebuilds the spanning tree.
We limit our discussion to the most widely used algorithm from~\citep{gower1969minimum}.
%
\section{Clustering Using Non-Parametric Entropy Estimates}
In general, the goal of clustering can be formulated as follows: 
given a finite collection of samples $\mathbf{x} = (x_1, \dotsc, x_n)$, we want to 
assign cluster-memberships $\mathbf{y} = (y_1, \dotsc, y_n ), y_i \in \{1, \dotsc k\}$ to these samples.
%
We adopt the viewpoint of information theoretic clustering of \citet{gokcay2002information}, 
where the $x_i$ are considered i.i.d{.} samples from a distribution $p(X)$, and the 
$y_i$ are found such that the mutual information $I(X, Y)$ between the distribution $p(X)$ and the
assigned labels $p(Y)$ is maximized.
We can rewrite this objective as 
\begin{align}
         I(X, Y)
        &= D_{\text{KL}}(p(X, Y) \parallel p(X) p(Y)) = H(X) - \sum_{y=1}^k p(Y{=}y) H(X \given Y {=} y)
\end{align}
where
\begin{itemize}
\item $\displaystyle D_\text{KL}\, = \int_\mathcal{X} p(X) \ln\left(\frac{p(X)}{q(X)}\right)\,dX$ is the Kullback-Leibler divergence,
\item $\displaystyle H(X)\, = \int_\mathcal{X} p(X) \ln(p(X))\,dX$ is the differential entropy, and
\item $\displaystyle H(X \given Y{=}y)\, = \int_\mathcal{X} p(X \given Y {=}y) \ln(p(X \given Y {=} y))\,dX$ is the conditional differential entropy.
    \end{itemize}
Expressing the mutual information in terms of the entropy is convenient, since
the objective then decomposes over the values of $Y$. 
%
Additionally, $H(X)$ is independent of the distribution of $Y$ and therefore
does not influence the search over $\mathbf{y}$.

>>>>

Clustering algorithms based on minimum spanning trees have been studied early
on in the statistics community, due to their efficiency.  One of the earliest
methods is single-link agglomerative clustering~\citep{gower1969minimum}.
Single-link agglomerative clustering can be understood as a minimum spanning
tree-based approach in which the largest edge is removed until the desired
number of components is reached.  \citet{zahn1971graph} refines this criterion
by cutting edges that are longer than other edges in the vicinity. This
approach requires tuning several constants by hand. More recently,
\citet{grygorash2006minimum} proposed a hierarchical MST-based clustering
approach that iteratively cuts edges, merges points in the resulting
components, and rebuilds the spanning tree.
We limit our discussion to the most widely used algorithm from~\citep{gower1969minimum}.
%
\section[Clustering Using Non-Parametric Entropy Estimates]{Clustering Using\linebreak Non-Parametric Entropy Estimates}
In general, the goal of clustering can be formulated as follows: 
given a finite collection of samples $\mathbf{x} = (x_1, \dotsc, x_n)$, we want to 
assign cluster-memberships $\mathbf{y} = (y_1, \dotsc, y_n ), y_i \in \{1, \dotsc k\}$ to these samples.
%
We adopt the viewpoint of information theoretic clustering of \citet{gokcay2002information}, 
where the $x_i$ are considered i.i.d{.} samples from a distribution $p(X)$, and the 
$y_i$ are found such that the mutual information $I(X, Y)$ between the distribution $p(X)$ and the
assigned labels $p(Y)$ is maximized.
We can rewrite this objective as 
\begin{align}
         I(X, Y)
        &= D_{\text{KL}}(p(X, Y) \parallel p(X) p(Y)) = H(X) - \sum_{y=1}^k p(Y{=}y) H(X \given Y {=} y)
\end{align}
where
\begin{itemize}
\item $\displaystyle D_\text{KL}\, = \int_\mathcal{X} p(X) \ln\left(\frac{p(X)}{q(X)}\right)\,dX$ is the Kullback-Leibler divergence,
\item $\displaystyle H(X)\, = \int_\mathcal{X} p(X) \ln(p(X))\,dX$ is the differential entropy, and
\item $\displaystyle H(X \given Y{=}y)\, = \int_\mathcal{X} p(X \given Y {=}y) \ln(p(X \given Y {=} y))\,dX$ is the conditional differential entropy.
    \end{itemize}
Expressing the mutual information in terms of the entropy is convenient, since
the objective then decomposes over the values of $Y$. 
%
Additionally, $H(X)$ is independent of the distribution of $Y$ and therefore
does not influence the search over $\mathbf{y}$.

### 2013-09-20 nyu/paper.tex
Helvetica, Titel neu setzen, korrekturen einarbeiten.

\section{Learning Depth-Sensitive Conditional Random Fields}\seclabel{learning}
We take a CRF approach, whose nodes represent a labeling of
superpixels.  We use an energy consisting of first and second order factors
(also called unary and pairwise potentials), with learned potential functions.
Let us denote the representation of an input image by $x$ and a labeling of
superpixels into semantic classes by $y$.  Then the general form of the energy is
\begin{equation}\eqlabel{energy}
    g(x, y) = \sum_{v \in V} \psi_v(x, y_v) + \sum_{(v, w) \in E} \psi_{v,w}(x, y_{v}, y_{w}).
\end{equation}
Here $V$ enumerates the superpixels, and $E\subset V \times V$ is a set of
edges, encoding adjacence between superpixels.

>>>>

\section[Learning Depth-Sensitive Conditional Random Fields]{Learning Depth-Sensitive\linebreak Conditional Random Fields}\seclabel{learning}
We take a CRF approach, whose nodes represent a labeling of
superpixels.  We use an energy consisting of first and second order factors
(also called unary and pairwise potentials), with learned potential functions.
Let us denote the representation of an input image by $x$ and a labeling of
superpixels into semantic classes by $y$.  Then the general form of the energy is
\begin{equation}\eqlabel{energy}
    g(x, y) = \sum_{v \in V} \psi_v(x, y_v) + \sum_{(v, w) \in E} \psi_{v,w}(x, y_{v}, y_{w}).
\end{equation}
Here $V$ enumerates the superpixels, and $E\subset V \times V$ is a set of
edges, encoding adjacence between superpixels.

### 2013-09-20 partial_supervision/paper.tex
Helvetica, Titel neu setzen, korrekturen einarbeiten.

\chapter{Weakly Supervised Object Segmentation}\label{ch:semi_supervised}

@@

Recently, several approaches have been proposed for semi-supervised semantic
segmentation.  While these are close to our work, there are several important
distinctions.  We address the task of object-class segmentation, that concerns
object categories, while semantic segmentation approaches often focus on
"stuff" categories like "sky" and "road" that are more easily detected using
simple texture features.
Additionally, in contrast to, for example, \citet{vezhnevets2011weakly}, our approach is in
principle applicable to large datasets, the regime where weak annotation is
most useful.

@@

We normalize the kernel $k_{MI}$ \citep{gaertner2002multi} using
\begin{equation}
k(X,X') := \frac{k_{MI}(X,X')}{\sqrt{k_{MI}(X,X)k_{MI}(X',X')}}.
\end{equation}
Training an SVM with this kernel produces a bag-level classifier for each
class, which we refer to as MIK\@.  This procedure is very efficient since
the resulting kernel matrix is of size of the number of bags, which is much smaller
than a kernel matrix of size of the number of instances, as is commonly used in the
literature~\citep{andrews2003support,nguyen2010new,zhang2008m3miml}.  Another
advantage over other methods is that it uses a single convex optimization,
whereas other approaches often use iterative
algorithms~\citep{andrews2003support} or need to fit complex probabilistic
models~\citep{zha2008joint}.

@@

\begin{figure}[tbp]
	\begin{center}
        \includegraphics[width=\linewidth]{images/scheme-crop.pdf}
	\end{center}
        \caption{Overview of our method. See text for details.}
	\figlabel{results}
\end{figure}

@@

\begin{table}
    \centering
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}p{208pt}ccc}
    \toprule
                & car & bike & person \\
    \cmidrule{2-4}
        This work&   0.30&  0.45&  0.43 \\
        Best strongly supervised approaches~\citep{fulkerson2009class,schulz2011}&   0.72&  0.72&  0.66 \\
    \bottomrule
    \end{tabularx}
    \caption{Pixel-level accuracy on the Graz-02 dataset.
        \tablabel{tab:graz}}
\end{table}

>>>>

\chapter[Weakly Supervised Object Segmentation]{Weakly Supervised\linebreak Object Segmentation}\label{ch:semi_supervised}

@@

Recently, several approaches have been proposed for semi-supervised semantic
segmentation.  While these are close to our work, there are several important
distinctions.  We address the task of object-class segmentation, that concerns
object categories, while semantic segmentation approaches often focus on
"stuff" categories like "sky" and "road" which are more easily detected using
simple texture features.
Additionally, in contrast to, for example, \citet{vezhnevets2011weakly}, our approach is in
principle applicable to large datasets, the regime where weak annotation is
most useful.

@@

We normalize the kernel $k_{MI}$ \citep{gaertner2002multi} using
\begin{equation}
k(X,X') := \frac{k_{MI}(X,X')}{\sqrt{k_{MI}(X,X)k_{MI}(X',X')}}.
\end{equation}
Training an SVM with this kernel produces a bag-level classifier for each
class, which we refer to as MIK\@.  This procedure is very efficient since
the resulting kernel matrix is of size of the number of bags, which is much smaller
than a kernel matrix of size of the number of instances, as is commonly used in the
literature~\citep{andrews2003support,nguyen2010new,zhang2008m3miml}. Another
advantage over other methods is the use of a single convex optimization,
whereas other approaches often use iterative
algorithms~\citep{andrews2003support} or need to fit complex probabilistic
models~\citep{zha2008joint}.

@@

\begin{figure}[tbp]
	\begin{center}
        \includegraphics[width=\linewidth]{images/scheme-crop.pdf}
	\end{center}
        \caption{Schematic overview. See text for details.}
	\figlabel{results}
\end{figure}

@@

\begin{table}
    \centering
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}p{208pt}ccc}
    \toprule
                & car & bike & person \\
    \cmidrule{2-4}
        MIL-MKL (our approach)&   0.30&  0.45&  0.43 \\
        Best strongly supervised approaches~\citep{fulkerson2009class,schulz2011}&   0.72&  0.72&  0.66 \\
    \bottomrule
    \end{tabularx}
    \caption{Pixel-level accuracy on the Graz-02 dataset.
        \tablabel{tab:graz}}
\end{table}

### 2013-09-20 structured_prediction/paper.tex
minor fixes
Helvetica, Titel neu setzen, korrekturen einarbeiten.

\chapter{Learning Conditional Random Fields}\label{ch:structured_pystruct}

@@

\pagebreak %FIXME maybe?

@@

\section{Learning Algorithms for Max-Margin Structured Prediction}\seclabel{learning_algorithms}

>>>>

\chapter[Learning Conditional Random Fields]{Learning\linebreak[4] Conditional Random Fields}\label{ch:structured_pystruct}

@@

\pagebreak

@@

\section{Learning Max-Margin Structured Prediction}\seclabel{learning_algorithms}
